Conceptualizing open health data platforms for low- and middle income countries

### 2024-04-02 index.qmd
Fix openhim image

- Since we use FHIR, we don't need a semantic layer because that is already provided
-

>>>>

- Since we use FHIR, we don't need a semantic layer because that is already provided
- We do need different semantic layer, namely with metrics. Explain different types of semantics.
  - The metrics layer same function as CQL. Discuss CQL vs generic metrics layer.
